### 2016-12-13 poster/poster.tex
poster update (dev experience, hardware, function call table template)

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath,amssymb}
\usepackage{setspace}

@@

%% BOX 0
\headerbox{Logos \& Graphs}{name=results,column=1,row=0.00, span=1}{
\includegraphics[width=.24\columnwidth]{graphics/TensorFlow.png}
\includegraphics[width=.24\columnwidth]{graphics/theano.jpeg}
\includegraphics[width=.24\columnwidth]{graphics/DyNet.pdf}
}

@@

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.69, span=1}{
\color{black}
Implementing stuff sucked/was great/was average
}

@@

%% BOX 0
\headerbox{Results}{name=results,column=2,row=0, span=1}{
\begin{itemize}
\item Time per epoch (for each system)
\item Time per batch
\item Most used function/ most resources consumed by (for each system)
\item Metrics for that function (possibly others that are shared?)
\item Time to create computation graph
\end{itemize}

>>>>

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{tabularx}

@@

%% BOX 0
\headerbox{Hardware}{name=methods,column=1,row=0.00,span=1}{
\vspace{0.5em}
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
\item \textbf{CPU}: Intel Core i7-5930K, 6 core, 12 thread (3.5 GHz)
\item \textbf{Memory}: G.SKILL Ripjaws 4 Series (8 x 8 GB)
\item \textbf{GPU}: GeForce GTX TITAN X (2 x 12 GB)
\end{itemize}

TODO: maybe convert into methodology section -- what experiments we ran
(until convergence, single epoch, single batch)
}

\headerbox{Logos \& Graphs}{name=results,column=1,row=0.30, span=1}{
\includegraphics[width=.24\columnwidth]{graphics/TensorFlow.png}
\includegraphics[width=.24\columnwidth]{graphics/theano.jpeg}
\includegraphics[width=.24\columnwidth]{graphics/DyNet.pdf}

% placeholdering for more appropriate graph
Total runtime on various subtasks:

\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & 6h57' &  \\
Test epoch & & 7'45'' & \\
Train batch & & 5'' &  \\
Test batch & & $<$1'' & \\
\end{tabular}
}

@@

%% Box 3
\headerbox{Development experience}{name=methods,column=1,row=0.65, span=1}{
\setlength{\extrarowheight}{3pt}
\begin{tabularx}{\textwidth}{l|X|X}
\textbf{Framework}  & \textbf{Pros} & \textbf{Cons} \\
\hline
TensorFlow   & Easy to use; good support for RNNs and language models &
    Symbolic computation graph is hard to debug; seems slower than others \\
\hline
Theano  & ``Lower level'' operations $\rightarrow$ highly customizable &
    No built-in support for RNNs (either need to implement or use a wrapper like Keras) \\
\hline
DyNet   & TODO   & TODO \\
\end{tabularx}
}

@@

%% BOX 0
\headerbox{Function calls}{name=results,column=2,row=0, span=1}{
%\begin{itemize}
%\item Time per epoch (for each system)
%\item Time per batch
%\item Most used function/ most resources consumed by (for each system)
%\item Metrics for that function (possibly others that are shared?)
%\item Time to create computation graph
%\end{itemize}

As expected for neural networks, most of the runtime is spent in
matrix multiplication (variants of \texttt{magma\_lds128\_sgemm\_kernel}).

\vspace{1em}

\begin{tabularx}{\textwidth}{l|r}
\textbf{Framework}  & \textbf{Percent time spent in matrix multiply} \\
\hline
TensorFlow  &  ... \\
Theano  & ... \\
DyNet   & ... \\
\end{tabularx}

TODO: discuss metrics for each.
}
